%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Application Programmer} % Job title
    {San Diego Super Computer Center} % Organization
    {San Diego, CA} % Location
    {July. 2018 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a \textbf{Python Flask} based web application for a fleet of internet monitoring tools that greatly simplifies keeping track of issues and getting information on them.}
        \item {Converted the barebones codebase from a previous Django attempt to \textbf{Flask} while adding login, comments, search, editing of info, and problem reporting functionality}
        \item {Learned and used \textbf{SQLAlchemy} for the login system and \textbf{SQLite} for monitoring tool info.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Application Programmer} % Job title
    {University of California, San Diego} % Organization
    {San Diego, CA} % Location
    {June. 2017 - June. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Continued research project from previous summer.}
        \item {Added more firewall rules matching functionality.}
        \item {Made secure, \textbf{RSA} based, signature checking functionality to rules list to prevent tampering, which is then output as a json based config file.}
        \item {Implemented \textbf{Python} plugin functionality for custom firewall rule matching.} \end{cvitems}
    }

%---------------------------------------------------------
  %\cventry
  
  %---------------------------------------------------------
  \cventry
    {Undergraduate Research Assistant} % Job title
    {University of California, San Diego} % Organization
    {San Diego, CA} % Location
    {June. 2016 - September. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on research with a Professor to create a \textbf{Python} based network firewall application that using  a commodity network switch, is able to have the performance of a dedicated firewall appliance.}
        \item {Used an \textbf{OpenFlow} based framework called \textbf{Ryu} to talk to the switch and implement rules for when to accept traffic.}
        \item {Made the configuration files for traffic rules easy to understand from someone who has setup firewalls on \textbf{Linux}
before}  \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
